OptiFit: an improved method for fitting amplicon sequences to existing OTUs

### 2021-10-22 paper/paper.Rmd
Don't include assert_that() code chunks

```{r deps, message = FALSE}
library(assertthat)
library(cowplot)
library(glue)
library(here)
library(knitr)
library(schtools)
library(tidyverse)
set.seed(20210624)
snakemake <- params$snakemake
if (is_character(snakemake)) {
  stop("You need to knit this R Markdown document from the Snakemake workflow")
}
load(here("results", "stats.RData"))

@@

```{r db_names}
db_names <- names(dn_dbs_mcc)
db_names_upper <- case_when(db_names == 'gg' ~ 'Greengenes', 
                           TRUE ~ toupper(db_names))
close_enough(dn_dbs_mcc['gg'], dn_dbs_mcc['silva'])
close_enough(dn_dbs_mcc['gg'], dn_dbs_mcc['rdp'], 10^-1)
mcc_decreasing <- c(closed_fit_rdp_mcc, closed_fit_silva_mcc, closed_fit_gg_mcc,
                    open_fit_silva_mcc, open_fit_gg_mcc, open_fit_rdp_mcc, 
                    opticlust_mcc)
assert_that(!is.unsorted(mcc_decreasing))
```

@@

```{r}
assert_that(!is.unsorted(c(frac_fit_rdp, frac_fit_silva, frac_fit_gg)))
assert_that((frac_fit_gg - frac_fit_silva) < 10)
assert_that((frac_fit_gg - frac_fit_rdp) > 40)
```

@@

```{r}
assert_that(!is.unsorted(c(closed_fit_silva_human_sec, 
                           opticlust_human_sec,
                           open_fit_silva_human_sec)))
```

@@

```{r}
assert_that(mcc_closed_fit_db_vs_vsearch > 10)
assert_that(frac_vsearch_vs_fit > 10)
assert_that((open_fit_gg_mcc - open_vsearch_mcc) > 0.20)
assert_that((sec_vsearch_vs_open_fit_db - sec_closed_fit_db_vs_vsearch) < 5)
```

@@

```{r}
close_enough(mcc_opticlust_vs_fit_split_simple, 0.02)
assert_that((frac_fit_split - frac_fit_gg) > 20)
assert_that(!is.unsorted(c(sec_closed_fit_split_vs_db, sec_closed_fit_db_vs_clust, sec_open_fit_split_vs_clust, sec_open_fit_split_vs_db)))
```

@@

```{r results_split, fig.dim=figs('results_split', 'dim'), fig.cap=figs('results_split', 'cap')}
figs('results_split', 'path') %>% 
  tiff::readTIFF() %>% 
  grid::grid.raster() 
```
```{r}
close_enough(cv_fit_split_mcc_human_simple, 0, tol = 10^-3)
assert_that(sec_fit_split_human_simple_1 > sec_fit_split_human_simple_9)
assert_that(frac_fit_split_human_simple_1 < frac_fit_split_human_simple_9)
```

@@

```{r}
close_enough(c(mcc_fit_split_simple, mcc_fit_split_abun), mcc_fit_split_dist)
assert_that(sec_fit_split_dist < sec_fit_split_abun & sec_fit_split_abun < sec_fit_split_simple)
close_enough(frac_fit_split_simple, frac_fit_split_abun)
assert_that(frac_fit_split_dist < frac_fit_split_simple)
```

@@

```{r}
ref_seqs <- read_tsv(here('subworkflows', '0_prep_db', 'data', 
                          'seq_counts.tsv')) %>% 
  pivot_wider(names_from = ref, values_from = nseqs) %>% as.list()
assert_that(ref_seqs[['rdp']] < ref_seqs[['silva']])
assert_that(ref_seqs[['silva']] < ref_seqs[['gg']])
```

>>>>

```{r deps, include=FALSE, message = FALSE}
library(assertthat)
library(cowplot)
library(glue)
library(here)
library(knitr)
library(schtools)
library(tidyverse)
set.seed(20210624)
snakemake <- params$snakemake
if (is_character(snakemake)) {
  stop("You need to knit this R Markdown document from the Snakemake workflow")
}
load(here("results", "stats.RData"))

@@

```{r db_names, include = FALSE}
db_names <- names(dn_dbs_mcc)
db_names_upper <- case_when(db_names == 'gg' ~ 'Greengenes', 
                           TRUE ~ toupper(db_names))
close_enough(dn_dbs_mcc['gg'], dn_dbs_mcc['silva'])
close_enough(dn_dbs_mcc['gg'], dn_dbs_mcc['rdp'], 10^-1)
mcc_decreasing <- c(closed_fit_rdp_mcc, closed_fit_silva_mcc, closed_fit_gg_mcc,
                    open_fit_silva_mcc, open_fit_gg_mcc, open_fit_rdp_mcc, 
                    opticlust_mcc)
assert_that(!is.unsorted(mcc_decreasing))
```

@@

```{r, include = FALSE}
assert_that(!is.unsorted(c(frac_fit_rdp, frac_fit_silva, frac_fit_gg)))
assert_that((frac_fit_gg - frac_fit_silva) < 10)
assert_that((frac_fit_gg - frac_fit_rdp) > 40)
```

@@

```{r, include = FALSE}
assert_that(!is.unsorted(c(closed_fit_silva_human_sec, 
                           opticlust_human_sec,
                           open_fit_silva_human_sec)))
```

@@

```{r, include = FALSE}
assert_that(mcc_closed_fit_db_vs_vsearch > 10)
assert_that(frac_vsearch_vs_fit > 10)
assert_that((open_fit_gg_mcc - open_vsearch_mcc) > 0.20)
assert_that((sec_vsearch_vs_open_fit_db - sec_closed_fit_db_vs_vsearch) < 5)
```

@@

```{r, include = FALSE}
close_enough(mcc_opticlust_vs_fit_split_simple, 0.02)
assert_that((frac_fit_split - frac_fit_gg) > 20)
assert_that(!is.unsorted(c(sec_closed_fit_split_vs_db, sec_closed_fit_db_vs_clust, sec_open_fit_split_vs_clust, sec_open_fit_split_vs_db)))
```

@@

```{r results_split, fig.dim=figs('results_split', 'dim'), fig.cap=figs('results_split', 'cap')}
figs('results_split', 'path') %>% 
  tiff::readTIFF() %>% 
  grid::grid.raster() 
```
```{r, include = FALSE}
close_enough(cv_fit_split_mcc_human_simple, 0, tol = 10^-3)
assert_that(sec_fit_split_human_simple_1 > sec_fit_split_human_simple_9)
assert_that(frac_fit_split_human_simple_1 < frac_fit_split_human_simple_9)
```

@@

```{r, include = FALSE}
close_enough(c(mcc_fit_split_simple, mcc_fit_split_abun), mcc_fit_split_dist)
assert_that(sec_fit_split_dist < sec_fit_split_abun & sec_fit_split_abun < sec_fit_split_simple)
close_enough(frac_fit_split_simple, frac_fit_split_abun)
assert_that(frac_fit_split_dist < frac_fit_split_simple)
```

@@

```{r, include = FALSE}
ref_seqs <- read_tsv(here('subworkflows', '0_prep_db', 'data', 
                          'seq_counts.tsv')) %>% 
  pivot_wider(names_from = ref, values_from = nseqs) %>% as.list()
assert_that(ref_seqs[['rdp']] < ref_seqs[['silva']])
assert_that(ref_seqs[['silva']] < ref_seqs[['gg']])
```
